---
title: "Introduction to nbi"
output: github_document
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "vignettes"
    )
  })
description: >
  Start here if this is your first time using nbi.package. You'll learn what nbi data is, how to import data to begin working on it, and example of how this package should be used.
vignette: >
  %\VignetteIndexEntry{Introduction to nbi}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, setup, include=FALSE}
library(nbi.package)
library(dplyr)
data_folder <- paste(.libPaths(),"/nbi.package/", sep = "")
knitr::opts_knit$set(root.dir = data_folder)
```

NBI, or National Bridge Inventory, is a large collection of information obtained by the US government about bridges across the country. 
Examples of the type of information contained within this dataset are:

* Bridge location information
* Owner of and whoever is responsible for maintaining the bridge
* The type, size, and specific quality about the bridge
* Maintenance status of the bridge

## How to import data

The functions `get_state_data` and `get_country_data` both import data directly from the download page at https://www.fhwa.dot.gov/bridge/nbi/ascii.cfm. 

These functions share an input value, "year", which changes which year the information being imported was collected. `get_state_data` has a seperate input value called "state" which limits what information will be imported to whatever US state specified, this can either be the state initials (AL, MD) or the state name (Idaho). `get_country_data` has an input value called "non_highway" which includes information about non-highway and routes under bridges, the default is FALSE; to include this information, change the value to TRUE.

To use these functions, you have to create an empty value to pipe the information into, in the following examples, the value is nbi_data. 

```{r}
# nbi_data is the empty value being filled
# The state being read is "MD" or Maryland, and the year being read is 2023
nbi_data <- get_state_data(state = "MD", year = 2023)
```

It should be noted there are default values added to get_state_data when either of the values are unchanged, the default state for `get_state_data` is "Alabama" and the default year is 2024

```{r}
# The year being read is 2022, and the non-highway bridges are not being included
nbi_data <- get_country_data(year = 2022, non_highway = FALSE)
```

The default year of `get_country_data` is 2024, and the default value for non_highway is FALSE

## How to convert data

The majority of the functions listed in this package change the values of specific columns to a different data type. Most of the values are coded using a coding guide on the FHWA website. The functins uncode these data points by taking the numbers listed and using the coding system to turn them into words instead of numbers. In order to use these, you need to supply the function with the dataset you want to change, then pipe the information into a value, which could be a different or the same value. 

LatLong_conversion is a very useful function that recodes the latitude and longitude values into the decimal degrees format. Many visualization programs like Socrata can use latitude and longitude in decimal format to create a map of data points.

```{r}
# Creating nbi_data to save the get_state_data information into the global environment
nbi_data <- get_state_data()
# This converts the information from the value nbi_data into the value nbi_converted_data
nbi_converted_data <- LatLong_conversion(nbi_data)
nbi_converted_data %>% select(LAT_016:LONG_017) %>% slice_head(n = 10)
```

